Finite Time Analysis of Linear Stochastic Approximation

### 2017-05-01 prob.tex
latest

\item \label{matvar} The martingale difference sequences\footnote{$\EE{M_t|\F_{t-1}}=0$ and $\EE{N_t|\F_{t-1}}=0$} $M_t\eqdef A_t-A_P$ and $N_t\eqdef b_t-b$ associated with $A_t$ and $b_t$ satisfy the following

>>>>

q\item \label{matvar} The martingale difference sequences\footnote{$\EE{M_t|\F_{t-1}}=0$ and $\EE{N_t|\F_{t-1}}=0$} $M_t\eqdef A_t-A_P$ and $N_t\eqdef b_t-b$ associated with $A_t$ and $b_t$ satisfy the following
